Enhancement of SDR in Thessaloniki

### 2024-02-19 GHI_enh_03_process.tex
Commit 2024-01-31 14:13
Commit 2024-02-01 14:14
Commit 2024-02-08 13:10
Commit 2024-02-19 13:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-16}

@@

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
\end{verbatim}

@@

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
\end{verbatim}

@@

\begin{verbatim}
2024-01-16 09:31:56.9 athan@sagan GHI_enh_03_process.R 0.865834 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-19}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-448.24 -172.37  -59.22  113.90  892.70

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -1.126e+02  5.761e+01  -1.955   0.0514 .  
as.numeric(Date)  4.155e-07  4.624e-08   8.985   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 244.7 on 359 degrees of freedom
Multiple R-squared:  0.1836,    Adjusted R-squared:  0.1813 
F-statistic: 80.72 on 1 and 359 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-448.24 -172.37  -59.22  113.90  892.70

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -1.126e+02  5.761e+01  -1.955   0.0514 .  
ST_E_monthly$Date  4.155e-07  4.624e-08   8.985   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 244.7 on 359 degrees of freedom
Multiple R-squared:  0.1836,    Adjusted R-squared:  0.1813 
F-statistic: 80.72 on 1 and 359 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

\begin{verbatim}
2024-02-19 10:09:06.3 athan@tyler GHI_enh_03_process.R 2.125423 mins
\end{verbatim}
